Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-21 doc/PRF2022/PRF_main.tex
peter updated s.m.

%% ***** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

In both cases, $\dot \gamma$ is the shear rate.
The flow rate $\lambda \dot \gamma$  
was chosen so that \eqref{eq:tg_flow} has the same
rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a $TG$ cell $A$.

@@

Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
contain the fully-resolved time courses for free energy $F$,
alignment order $S_2$, and strain $E$. The eight setups
correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
and striated---and two background flows---shear and TG,
and the data are plotted with the same ordinate to facilitate
comparisons between simulation setups.  Each setup considers
a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses
in Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
contain significant oscillations due to the particle-based formulation
and tumbling inherent to the background flows.  To extract meaningful
data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
their time averate over the interval $t \in [0, T]$.

@@

\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

>>>>

%% ***** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-2}

@@

In both cases, $\dot \gamma$ is the shear rate.
The flow rate $\lambda \dot \gamma$  
was chosen so that \eqref{eq:tg_flow} has the same
rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a TG cell $A$.

@@

Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
contain the fully-resolved time courses for free energy $F$,
alignment order $S_2$, and strain $E$. The eight setups
correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
and striated---and two background flows---shear and TG,
and the data are plotted with the same ordinate to facilitate
comparisons between simulation setups.  Each setup considers
a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses
in Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
contain significant oscillations due to the particle-based formulation
and tumbling inherent to the background flows.  To extract meaningful
data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
their time average over the interval $t \in [0, T]$.

@@

\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:ulshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

### 2023-03-21 doc/PRF2022/Supplementary.tex
peter updated s.m.

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
configurations. The vesicle case undergoes tank-treading whereas the
initially disordered BC (i) case increases orientational order. The
multilamellar assemply behaves as a rigid body, and the striated
configuration moreso. No ruptures occur. \\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at low flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
for the striated configurations. The vesicle stays inact, whereas the
dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
striated assembly is basically rigid. \\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow at a higher shear rate. For the choices of the shear rate, we
pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the
bilayer, $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma =
0.15$ for the striated configurations. The time step of all simulations
is $\Delta t=0.2$. In this movie, some clear structural ruptures occur
in each case. In order to observe the structure behaviors at later time,
we stabilize the frame by tracking the center of mass position of all
JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at higher flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
striated configurations. Clear structural ruptures occur in each case.
In all cases, there is significant reduction in the orientational order
of the assemblies. While the BC (i) cases are broken into several
pieces, the main body of the BC (ii) and BC (iii) assemblies are not
pulled apart by the background flow.

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
\newpage

>>>>

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the bilayer, $\dot\gamma
= 0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
configurations. The vesicle case undergoes tank-treading whereas the
initially disordered BC (i) case increases orientational order. The
multilamellar assemply behaves as a rigid body, and the striated
configuration moreso. No ruptures occur. \\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at low flow rates. For the choices of the flow
strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$
for the striated configurations. The vesicle stays inact, whereas the
dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
striated assembly is basically rigid. \\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow at a higher shear rate. For the choices of the shear rate, we
pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma =
0.15$ ns$^{-1}$ for the striated configurations. The time step of all simulations
is $\Delta t=0.2$ ns$^{-1}$. In this movie, some clear structural ruptures occur
in each case. In order to observe the structure behaviors at later time,
we stabilize the frame by tracking the center of mass position of all
JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at higher flow rates. For the choices of the flow
strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
striated configurations. Clear structural ruptures occur in each case.
In all cases, there is significant reduction in the orientational order
of the assemblies. While the BC (i) cases are broken into several
pieces, the main body of the BC (ii) and BC (iii) assemblies are not
pulled apart by the background flow.\\

\noindent
{\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
The parameter $\lambda$ controls the cell size in Taylor-Green flow. 
$\lambda$ values are varied from 1.0 to 4.0 while the flow rate $\lambda\dot\gamma=0.1$ is fixed. There is a rotation transition from counterclockwise ($\lambda=1$ nm and  2 nm) to clockwise ($\lambda=3$ nm and 4 nm). \\

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
%\newpage
